Run the model

### 2019-11-20 scripts/3_model/2_run_model.Rmd
Updated figure names exported in the model Rmd

@@

@@

@@

@@

```{r}
#Paper export
ggsave(
  plot = allocation_cost_plot,
  filename = here("docs", "img", "allocation_cost_plot.pdf"),
  width = 5.5,
  height = 3.5
)
```

>>>>

```{r}
ggsave(plot = effort_and_revenues,
       file = here("docs", "img","effort_and_revenues_ED_Fig4.tiff"),
       width = 6,
       height = 4)
```

@@

```{r}
ggsave(plot = vessel_day_price_no_trading_plot,
       filename = here("docs", "img", "vessel_day_price_no_trading_plot_ED_Fig1.tiff"),
       width = 6,
       height = 3)
```

@@

```{r}
ggsave(plot = vessel_day_price_with_trading_plot,
       filename = here("docs", "img", "vessel_day_price_with_trading_plot_ED_Fig3.tiff"),
       width = 6,
       height = 4.5)
```

@@

```{r}
ggsave(plot = profits_PNA_notKIR_no_trading_plot,
       filename = here("docs", "img", "profits_PNA_notKIR_no_trading_plot_ED_Fig2.tiff"),
       width = 3,
       height = 3)
```

@@

```{r}
#Paper export
ggsave(
  plot = allocation_cost_plot,
  filename = here("docs", "img", "allocation_cost_plot.pdf"),
  width = 5,
  height = 3.5
)
```
